\documentclass{article}

\usepackage[multiple]{footmisc}

\begin{document}
\thispagestyle{empty}
\begin{centering}
{\Large Propositions}\\
\vspace{2em}
\textbf{\LARGE Eye to AI}\\
\textbf{\LARGE MR image analysis of glioma using machine learning}\\
\vspace{2em}
{\large by Sebastian R. van der Voort}\\
\end{centering}
\vspace{5em}
\begin{enumerate}
    \item A properly validated radiomics method is more valuable than one with high performance. (\textit{this thesis})
    \item Not all genetic features of a glioma cause a characteristic change in its appearance on MRI, invalidating a potential radiomics approach for these features. (\textit{this thesis})
    \item The analysis of glioma MR images is currently limited by the available knowledge of the disease mechanisms, not by the available imaging data. (\textit{this thesis})
    \item The lack of adequate metadata associated with brain MRI scans is currently inhibiting the automatic processing of these scans. (\textit{this thesis})
    \item The training of more extensive convolutional neural networks requires code optimisation rather than additional GPU resources. (\textit{this thesis})
    \item Confirmation bias leads to the publication of unreliable positive results.
    \item Reproducibility of a study requires code, data, trained models, and evaluated results to be shared publicly.
    \item Researchers will try to build a rocket ship without having invented a screwdriver.
    \item The need to back up every scientific statement with a citation leads to misrepresentations of research conclusions\footnote{\textit{S. Klein et al.}, \textbf{Elastix: A Toolbox for Intensity-Based Medical Image Registration}, 2010}\footnote{\textit{M. Smits et al.}, \textbf{Imaging of oligodendroglioma}, 2016}.
    \item Finding a lasting solution for environmental and societal issues requires science and scientists to be more approachable.
    \item Board games are an excellent opportunity to learn essential skills such as cooperation, communication, planning, and compassion.
\end{enumerate}


\end{document}
